Teaching a Class to Grade Itself using Game Theory

### 2013-09-22 Primes Write up.tex
Made revisions to a plethora of things.
Primarily, the Calibration Mechanism.

With this in mind, we set out to create a series of mechanisms that increase in complexity, as well as creating an ever-changing model. We start with a simple model and set of assumptions and gradually build upon this set to increase the realism of the model. After every change in assumptions, we create a new mechanism that applies to the new set of assumptions, and works effectively and efficiently. By the end of our research, we have contributed a highly realistic and detailed model that other game theorists can build off of to form their own solutions, as well as a set of realistic mechanisms that could be implemented in practice.
\section{Materials and Methods}
\subsection{The Scenario}
In order to find a solution to the professor’s problem, we consider the case of a single assingment. To apply our solution to an entire class, simply apply it to each assignment separately. In such a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers, $i$ has an objective score $o_i,~where~ 0\leq o_i \leq 100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way and output the grades. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, we create a simple set of assumptions:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
To re-express the above in mathematics:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
\end{enumerate}

@@

\subsection{Benchmark}
%Efficiency objective%
A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development. Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced. Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desired outcome. In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.

When creating this benchmark, there are 2 things that need to be considered: accuracy and workload. Accuracy is important because if we do not care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism. Secondly, caring about work done. If we do not care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.

In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done. The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is the following. Consider these two cases for the maximum deviation of the student-given grade to the hypothetical professor-given grade.
\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
\item Each of 1000 students should receive a 90, but their peers assigned them a 91. Maximum deviation is 1, sum is 1000.
\item Each of 1000 students should receive a 90. One person is assigned a 0, while everyone else is assigned a 90. Maximum deviation is 90, sum is 90.
\end{enumerate}
Clearly, case A is better than case B. The smaller maximum deviation for case A reflects this.
For the maximum work done, consider the the following cases:
\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
\item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
\item Each of 1000 students grades 2 papers. Maximum work is 2, sum is 2000.
\end{enumerate}
This time, case B is intuitively better than case A. Again, the smaller maximum deviation agrees.

@@

Now that a simple set of assumptions and a benchmark have been created, it becomes possible to create simple mechanisms, and improve upon them until we get to a final, satisfactory mechanism.

To improve upon our mechanisms, we need to often change our assumptions. This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex situations.

@@

\subsubsection{Process}
First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
\begin{definition}(Calibration Mechanism)
In this mechanism, the professor chooses one paper to grade, which he gives to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. Otherwise they get the minimum of an arbitrary number $m$ and the grade their assigned grade.
\end{definition}
\begin{theorem}
With this mechanism, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
\end{theorem}

\begin{proof}
Let $G$ be the maximum of \{some minimum value $m$, the assigned grade\}.
The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$, because the students have a 0.5 chance of getting a 0 and a 0.5 chance of getting $G$.

If a student grades both papers, his or her happiness will be equal to $H(G)-2$. Because the grader spent two units of energy, and are guaranteed to get $G$.

If a student grades neither, his or her happiness will be $H(0)$, because he or she automatically get a 0 but spend no energy.

This means that if $H(G) - 2 > H(0)$, then a student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(m) > H(0) + 2$.
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value $m$ high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
\end{proof}
\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}

\subsubsection{Benchmark and Remaining Issues}
Computed from the above, the objective function of this mechanism is 4 --- a very low value. A value of 4 is equivalent to if we convinced every student to accurately grade 4 papers.

@@

This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.

\subsection{Improved Calibration Mechanism}
\subsubsection{Process}
In the calibration mechanism, we assumed that students could not communicate with each other. For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the calibration mechanism on a larger scale. Every student grades the papers of $k$ other students. The professor also grades every $k$th paper, these are the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\begin{theorem}
In this mechanism, students will return accurate grades, even though they can communicate with each other.
\end{theorem}
\begin{proof}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as the minimum value is high enough, the papers will be accurately graded, as before.
\end{proof}
\subsubsection{Benchmark and Remaining Issues}
The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before. The huge problem with this is the high amount of work being done.

\emph{The benchmark results for The Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}

\subsection{The Deduction Mechanism}
\label{sec:deduction}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Process}
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0. To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$. (Then the student's grade is converted from Happiness to an actual score).
\end{definition}
\begin{theorem}
The addition of the contribution score being added or subtracted should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
\end{theorem}
\begin{proof}
The graders have two choices, they can either grade the papers, or not grade them.

@@

\end{proof}
\noindent
\emph{This process is summarized in Figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
\newline
\emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
\subsubsection{Benchmark}
In this model, the most work is being done by the students, who each grade 2 papers. In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper. This means that no papers will ever reach the professor, so he/she will not have to grade anything. Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades. This means that the final benchmark is $2+0=2$. This is the lowest out of all the mechanisms so far.
\subsection{Final Assumptions}
Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders. With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.

\begin{enumerate}[itemsep=0pt, parsep=0pt]
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where $g$ represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
\item For a given student in $N$, that student has contact with all other students in $N$
\end{enumerate}
\newpage
\section{Illustrations}
{
\noindent
\begin{figure}[!h]
	\centering
		\includegraphics[width=0.75\textwidth]{Comparison.eps}
		\caption {A comparison of mechanisms in terms of effectiveness and scalability.\label{fig:comparison}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
		\caption {A flowchart of the Calibration Mechanism (Section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
		\caption {A flowchart of the Deduction Mechanism (Section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
\end{figure}
}
\section{Discussion}
With this research, the goal was to create a mechanism that fulfilled our goal; incentivizing students to play the ``game'' to correctly grade the assignments of other students. The mechanism created by the end of the research was realistic enough to be implemented in a classroom environment where all students are capable of grading others assignments efficiently.

>>>>

With this in mind, we set out to create a series of mechanisms that increase in complexity, as well as an increasingly-realistic model. We start with a simple model and set of assumptions and gradually build upon this set to increase the realism of the model. After every change in assumptions, we create a new mechanism that applies to the new set of assumptions, and works effectively and efficiently. By the end of our research, we have contributed a highly realistic and detailed model that other game theorists can build off of to form their own solutions, as well as a set of realistic mechanisms that could be implemented in practice.
\section{Materials and Methods}
\subsection{The Scenario}
In order to find a solution to the professor's problem, we consider the case of a single assignment. To apply our solution to an entire class, simply apply it to each assignment separately. In such a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers, $i$ has an objective score $o_i,~where~ 0\leq o_i \leq 100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way and output the grades. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, we create a simple set of assumptions:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
To re-express the above in mathematics:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
\end{enumerate}

@@

\subsection{Benchmark}
%Efficiency objective%
A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development. Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced. Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desirable outcome. In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.

When creating this benchmark, there are 2 things that need to be considered: accuracy and workload. Accuracy is important because if we do not care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism. Secondly, ignoring the amount of work done means the professor grade can everything. This is bad because it makes the professor extremely unhappy.

In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done. The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is the following. Consider these two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade. Note that the grade the student receives at the end is not necessarily that given by their peers.
\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
\item Each of 1000 students should receive a 90, but the mechanism assigned a 91 to each of them. Maximum deviation is 1, sum is 1000.
\item Each of 1000 students should receive a 90. One person is assigned a 0, while everyone else is assigned a 90. Maximum deviation is 90, sum is 90.
\end{enumerate}
Clearly, case A is better than case B. The smaller maximum deviation for case A reflects this.
For the maximum work done, consider the the following cases:
\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
\item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
\item Each of 1000 students grades 2 papers. Maximum work is 2, sum is 2000.
\end{enumerate}
This time, case B is intuitively better than case A. Again, the benchmark captures our intuition.

@@

Now that we have created a simple set of assumptions and a benchmark, we can create several simple mechanisms, and improve upon them until we are satisfied with a final mechanism. In the improvement process, we gradually refine our assumptions to better represent reality. This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex yet more realistic situations.

@@

\subsubsection{Process}
First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
One idea is to have the professor choose one paper that he grades. He then distributes this paper to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. If they succeed, they receive their assigned grade.
This is almost exactly the Calibration Mechanism, except we make a small modification. Considering the idea as is, a student whose own grade on the assignment is a 0 has no incentive to grade the paper: Their grade will be a 0 whether or not they grade the paper, so why bother? To cope with this, we pick some minimum grade $m > 0$ and promise every student that they will receive a grade of at least $m$ if they grade the assignment correctly.
By appropriately choosing a value for $m$, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
\begin{definition}(Calibration Mechanism)
First, the professor pre-grades a paper $P$. Each student is asked to grade two papers: $P$ and another paper. If the student fails to grade $P$, he or she gets a zero. Otherwise, the student gets the maximum of some minimum value and his or her assigned grade.
\end{definition}
\begin{theorem}
If $m>H^{-1}(2)$, it will be in every student's best interest to grade both papers in the Calibration Mechanism.
\end{theorem}
\begin{proof}
Consider the student $i$.
If all other students behave as desired, student $i$ will be assigned a grade $G=max(m,o_i)$ unless he or she does not grade $P$ correctly.
The happiness of student $i$ grading one paper is $\frac{H(G)}{2}-1$, because the student has a 50\% chance of getting a 0 and a 50\% chance of getting $G$.
If student $i$ grades both papers, his or her happiness will be $H(G)-2$ because he or she is guaranteed to receive $G$ by grading both correctly.
If student $i$ grades neither, his or her happiness will be $0$, because he or she  spends no energy and gets a 0.
Therefore, if $H(G) > 2$, then student $i$ will grade both papers. So, for the professor to guarantee that the class use effort and obtain the correct grades, $H(m) > 2$.
Since we chose $m$ to be greater than $H^{-1}(2)$, the previous always holds.
\end{proof}
\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}

\subsubsection{Benchmark and Remaining Issues}
We now show that the Calibration Mechanism achieves a very low value in our benchmark.
\begin{theorem}
The Calibration Mechanism achieves a benchmark score of 4.
\end{theorem}
\begin{proof}
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value $m$ high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
\end{proof}

@@

This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.
%%%%%%%% Go over this section and try to make it similar to the above section. %%%%%%%%
\subsection{Improved Calibration Mechanism}
\subsubsection{Process}
In the calibration mechanism, we assumed that students couldn't communicate with each other, and therefore couldn't figure out which of the two papers they were asked to grade was calibrated. For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the Calibration Mechanism on a larger scale. Every student is put into a cycle. Each student grades the papers of $k$ next students. The professor also grades every $kth$ paper in the cycle, which become the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\begin{theorem}
In this mechanism, students will return accurate grades, even though they can communicate with each other.
\end{theorem}
\begin{proof}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as $m > H^{-1}(k)$, the papers will be accurately graded, as before.

\end{proof}
\subsubsection{Benchmark and Remaining Issues}
The amount of work done by the professor is $\frac{n}{k}$. For the students, this number is $k$. The maximum grade deviation is also $k$, for $m > H^{-1}(k)$. Therefore, the benchmark $max(k, \frac{n}{k}) + k$, a potentially higher value than before. The huge problem with this is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$. We can see that the benchmark becomes $2\sqrt{n}$.

\emph{The benchmark results for The Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
%%%%%%%% Revise this section to be like the above. %%%%%%%%
\subsection{The Deduction Mechanism}
\label{sec:deduction}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Process}
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives the incorrect grader(s) a 0. To compute the final score for a student, the final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$. (Then the student's grade is converted from Happiness to an actual score).
\end{definition}
\begin{theorem}
The addition of the contribution score being added or subtracted should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
\end{theorem}
\begin{proof}
The graders have two choices, they can either grade the papers, or not grade them.

@@

\end{proof}
\noindent
\emph{This process is summarized in Figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
\newline
\emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
\subsubsection{Benchmark}
In this model, the most work is being done by the students, who each grade 2 papers. In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper. This means that no papers will ever reach the professor, so he or she will not have to grade anything. Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades. This means that the final benchmark is $2+0=2$. This is the lowest out of all the mechanisms so far.
\subsection{Final Assumptions}
Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders. With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.

\begin{enumerate}[itemsep=0pt, parsep=0pt]
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where $g$ represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
\item For a given student in $N$, that student has contact with all other students in $N$
\end{enumerate}
\newpage
\section{Illustrations}
{
\noindent
%%%%%%%% Make sure the comparison chart shows 2*sqrt(n) %%%%%%%%
\begin{figure}[!h]
	\centering
		\includegraphics[width=0.75\textwidth]{Comparison.eps}
		\caption {A comparison of mechanisms in terms of effectiveness and scalability.\label{fig:comparison}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
		\caption {A flowchart of the Calibration Mechanism (Section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
		\caption {A flowchart of the Deduction Mechanism (Section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
\end{figure}
}
%%%%%%%% Go over this section, make edits and revise. %%%%%%%%
\section{Discussion}
With this research, the goal was to create a mechanism that fulfilled our goal; incentivizing students to play the ``game'' to correctly grade the assignments of other students. The mechanism created by the end of the research was realistic enough to be implemented in a classroom environment where all students are capable of grading others assignments efficiently.
